---
title: "Bank Marketing Campaign Analysis"
author: "Feiran Zhang"
date: "`r Sys.Date()`"
output: 
  html_document
---

```{r set-chunk-opts, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

# Introduction

This report analyzes a bank marketing campaign dataset containing information about clients contacted via phone calls to subscribe to term deposits. The dataset includes 4,521 observations with 17 variables capturing demographic information (age, job, marital status), financial status (balance, loans), and campaign details (contact type, duration, previous outcomes).

**Analysis Objectives**:
1. Explore subscription rates by job type
2. Visualize age distribution differences between subscribers and non-subscribers
3. Identify key demographic factors associated with term deposit subscriptions
```{r setup, include=FALSE}
library(tidyverse)
library(kableExtra)
library(here)

here::i_am("report/finalproject2.Rmd")
clean_data <- readRDS(
  file = here::here("output", "data_clean.rds")
)
```

# Descriptive Analysis

## Subscription Rates by Job Type

```{r, tables}
subscription_by_job <- readRDS(
  file = here::here("output/table_one.rds")
)

subscription_by_job %>%
  rename(
    `Job Category` = job,
    Subscription = y,
    Count = Count,
    `Percentage (%)` = Percentage
  ) %>%
  kable(
    caption = "Term Deposit Subscription Rates by Occupation",
    digits = 1,
    align = c("l", "c", "c", "c")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    font_size = 14,
    position = "center"
  ) %>%
  row_spec(0, bold = TRUE, color = "white", background = "#3498db") %>%
  column_spec(1, bold = TRUE) %>%
  footnote(
    general = "Data collected from a bank marketing campaign dataset",
    general_title = "Note:"
  )
```

### Table Description:
This table presents the distribution of term deposit subscriptions across different job categories. Blue-collar workers represent the largest group contacted (9,024 cases) but show a relatively low subscription rate. Management professionals have a relatively higher subscription count (1,301 cases). Students, despite having a smaller absolute count, exhibit the highest relative subscription rate, indicating a stronger interest in term deposits compared to other occupations. Retirees also have a notable subscription rate, potentially due to their financial planning needs.

# Graphical Analysis

## Age Distribution by Subscription Status

```{r, figure}
#| fig.align = "center",
#| out.width = "800px"
knitr::include_graphics(
  here::here("output/histogram.png")
)
```

### Figure Description:
The histogram illustrates the age distribution of clients who were contacted during the campaign, categorized by subscription status. The majority of non-subscribers (shown in red) are in the 25-45 age range, while a significant portion of subscribers (shown in blue) are observed in the 25-35 and 55-65 age groups. This suggests that younger professionals and pre-retirees may be more likely to subscribe to term deposits. The overall distribution is skewed towards younger clients, but the relative proportion of subscriptions increases for older age brackets.